Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction

### 2019-03-17 Manuscript_draft/Tables_and_figures.Rmd
edits panel family effect sizes

@@

pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,aes(color=factor(Family))) + theme(legend.title = element_blank(),legend.direction="horizontal")+
  geom_linerange(size=0.6,linetype=1, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

pp2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

>>>>

pp1<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("A)",italic(' B. oleracea'))))

pp2<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("B)",italic(' B. rapa'))))

p3<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("C)",italic(' E. sativa'))))

p4<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("D)",italic(' S. alba'))))

p5<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("E)",italic(' I. aquatica'))))

p6<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("F)",italic(' I. purpurea'))))

p7<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("G)",italic(' C. annuum'))))

p8<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("H)",italic(' P. integrifolia'))))

p9<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("I)",italic(' S. lycopersicum'))))

@@

p10<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,aes(color=factor(Family))) + theme(legend.title = element_blank(),legend.direction="horizontal")+
  geom_linerange(size=0.6,linetype=1, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena'))))
